Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality

### 2024-09-08 paper/ms.tex
Add images to results

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\kms}{\ensuremath{\textrm{km}/\textrm{s}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\OFe}{\ensuremath{[\textrm{O}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
\newcommand{\dex}{\ensuremath{\textrm{dex}}}
\newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}

@@

>>>>

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\ckpc}{\ensuremath{\textrm{ckpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\kms}{\ensuremath{\textrm{km}/\textrm{s}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\OFe}{\ensuremath{[\textrm{O}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
\newcommand{\dex}{\ensuremath{\textrm{dex}}}
\newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}

@@

\subsection{Images}\label{ssec:images}
\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/images_star.pdf}
  \caption{Surface density projections of star particles in our SoI at the transition between the high- and low-$\alpha$ sequences. Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right. Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, bar strength ($A_{2,\textrm{max}}$), and BH accretion rate. A guide is given in the top left subpanel. At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
  \label{fig:images_star}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/images_gas.pdf}
  \caption{As in Figure~\ref{fig:images_star}, but showing the surface density projections of gas in our SoI at the transition between the high- and low-$\alpha$ sequences. Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right. Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, gas fraction, and BH accretion rate. A guide is given in the top left subpanel. At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
  \label{fig:images_gas}
\end{figure*}

In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts. In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$. Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square. All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used. Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$).

We also show four relevant statistics in each panel of Figures~\ref{fig:images_star} and \ref{fig:images_gas}. For Figure~\ref{fig:images_star}, these are, clockwise from the upper left, the SFR, cosmic time, bar strength, and BH accretion rate. They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).

A description of the events portrayed in each Figure is given in Section~\ref{ssec:cause_qui}.
